Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
rename figures

\vspace{-.8cm}
\enlargethispage{.3cm}

@@

This paper focuses on a surprising construction of the associahedron that recently appeared in mathematical physics.
Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces and produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
Starting from an acyclic initial seed~$\seed_\circ$, they consider a certain set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, that can be interpreted as linear spaces in~$\R^\c{V}$.
Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.

\medskip
In this paper, we revisit, extend and explore further this construction using a reversed approach.
Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
This type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
Our approach is based on an elementary but powerful observation: if the type cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach enables us to efficiently revisit and extend the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
This new perspective has several advantages, as our proof uniformly applies to:

\smallskip
\begin{itemize}
\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic). In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.

@@

\smallskip
\item \textbf{any positive real valued parameters}, regardless of whether they are rational or not. In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
\end{itemize}

\smallskip
\noindent
These advantages all follow from one essential feature of our reversed approach.
Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
\begin{itemize}
\item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
For this, we use representation theory in the setting of~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).

\smallskip
\item On the \textbf{geometric side}, we use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{sec:typeCone}). We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
\end{itemize}

@@

\smallskip
\begin{itemize}
\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.  These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}. It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra. Even for finite non-kissing complexes, it turns out that the type cone of the non-kissing fan is not always simplicial (see \cref{exm:nonSimplicialTypeConeNKC}). We prove however that the type cone is always simplicial when the gentle bound quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no oriented cycle of length~$2$). Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations. We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}). Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex. We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for arbitrary brick algebras based on extriangulated categories (see \cref{sec:extricats}).

\medskip
\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}. As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra. The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}. Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}. All these realizations have the same normal fan, called nested fan. We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier. For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities. In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path). Our results describe nevertheless all polytopal realizations of the graphical nested fans.
\end{itemize}

\smallskip
\enlargethispage{.3cm}
Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
We believe that this gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
Tempting candidates are quotientopes for hyperplane arrangements beyond type~$A$, which are particularly interesting since the coarsenings of a fan essentially correspond to the faces of its type cone (see \cref{subsec:facesTypeCone}).

@@

\smallskip
\begin{itemize}
\item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences. While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)). It would be particularly interesting to fully understand these specific mutations for arbitrary ($\tau$-tilting finite) gentle algebras.

\smallskip
\item The rays of the type cone of~$\Fan$ correspond to specific polytopes which form a positive Minkowski basis of all realizations of~$\Fan$ (see \cref{subsec:MinkowskiSums}). In particular, when the type cone is simplicial, any polytopal realization of~$\Fan$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of the polytopes corresponding to the rays of the type cone. For cluster algebras, it follows from~\cite[Sect.~6]{BazierMatteDouvilleMousavandThomasYildirim} that these polytopes are Newton polytopes of the $F$-polynomials. It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle algebras.
\end{itemize}

>>>>

\vspace{-1cm}
\enlargethispage{.5cm}

@@

This paper focuses on a surprising construction of the associahedron that recently appeared in mathematical physics.
Motivated by the prediction of the behavior of scattering particules, N.~Arkani-Hamed, Y.~Bai, S.~He, and G.~Yan recently described in~\cite[Sect.~3.2]{ArkaniHamedBaiHeYan} the kinetic associahedron.
It is a class of polytopal realizations of the classical associahedron obtained as sections of a high-dimensional positive orthant with well-chosen affine subspaces.
This construction provides a large degree of freedom in the choice of the parameters defining these affine subspaces and produces all polytopes whose normal fan is affinely equivalent to that of J.-L.~Loday's associahedron~\cite{Loday} (see \cref{subsec:typeConeAsso}).
These realizations were then extended by V.~Bazier-Matte, G.~Douville, K.~Mousavand, H.~Thomas and E.~Yildirim~\cite{BazierMatteDouvilleMousavandThomasYildirim} in the context of finite type cluster algebras using tools from representation theory of quivers.
More precisely, they fix a finite type cluster algebra~$\c{A}$ and consider the real euclidean space~$\R^\c{V}$ indexed by the set~$\c{V}$ of cluster variables of~$\c{A}$.
Starting from an acyclic initial seed~$\seed_\circ$, they consider a set~$\c{M}$ of mesh mutations and compute the corresponding linear dependences between the $\b{g}$-vectors, that can be interpreted as linear spaces in~$\R^\c{V}$.
Finally, they perturb these mesh linear spaces by a collection~$\b{\ell} \in \R^{\c{M}}$ of positive parameters and intersect the resulting perturbed mesh affine spaces with the positive orthant of~$\R^\c{V}$ (see \cref{subsec:typeConeCA}).
They show that the resulting polytope is always a generalized associahedron, and that its normal fan is the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$.
A by-product of their construction is that the space of all polytopal realizations of the $\b{g}$-vector fan of~$\c{A}$ with respect to the initial acyclic seed~$\seed_\circ$ is a simplicial cone.

\medskip
\enlargethispage{.5cm}
In this paper, we revisit, extend and explore further this construction using a reversed approach.
Given a complete simplicial fan~$\Fan$, we consider the space~$\typeCone(\Fan)$ of all its polytopal realizations, called type cone of~$\Fan$ in~\cite{McMullen-typeCone}.
This type cone is known to be a polyhedral cone defined by a collection of inequalities corresponding to the linear dependences among the rays of~$\Fan$ contained in pairs of adjacent maximal cones of~$\Fan$ (see \cref{def:typeCone}).
Our approach is based on an elementary but powerful observation: if the type cone~$\typeCone(\Fan)$ is a simplicial cone, then all polytopal realizations of~$\Fan$ can be described as sections of a high dimensional positive orthant with a collection of affine subspaces corresponding to the facets of~$\typeCone(\Fan)$ (see \cref{coro:simplicialTypeCone}).
To prove that the type cone~$\typeCone(\Fan)$ is simplicial, we just need to identify which pairs of adjacent maximal cones of~$\Fan$ correspond to the facets of~$\typeCone(\Fan)$ and to show that the corresponding linear dependences among their rays positively span the linear dependence among the rays of any pair of adjacent maximal cones of~$\Fan$.
When applied to the $\b{g}$-vector fans of cluster algebras (see \cref{subsec:typeConeCA}), this reversed approach enables us to efficiently revisit and extend the construction of~\cite{BazierMatteDouvilleMousavandThomasYildirim}.
This new perspective has several advantages, as our proof uniformly applies to:

\smallskip
\begin{enumerate}[$\quad\bullet$]
\item \textbf{any initial seed}, regardless of whether it is acyclic or not (see \cref{exm:typeConeCA,fig:clusterFans,fig:labelFacetDefiningInequalititiesCA1,fig:labelFacetDefiningInequalititiesCA2} for examples in types~$A_3$ and~$C_3$~cyclic). In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} only treats acyclic initial seeds.

@@

\smallskip
\item \textbf{any positive real valued parameters}, regardless of whether they are rational or not. In contrast, the proof of~\cite{BazierMatteDouvilleMousavandThomasYildirim} naturally applies to rational parameters and then requires to apply an approximation argument.
\end{enumerate}

\smallskip
\noindent
\enlargethispage{.3cm}
These advantages all follow from one essential feature of our reversed approach.
Namely, it enables to completely separate the algebraic aspects from the geometric aspects of the problem:
\begin{enumerate}[$\quad\bullet$]
\item On the \textbf{algebraic side}, we study the relations between the $\b{g}$-vectors of a finite type cluster algebra and we show that the mesh mutations minimally generate these relations.
For this, we use representation theory in the setting of~$2$-Calabi--Yau triangulated categories, and we adapt M.~Auslander's proof that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type~\cite{Auslander1984} (see \cref{sec:clusterCategories}).

\smallskip
\item On the \textbf{geometric side}, we use elementary manipulations to show that a fan whose type cone is simplicial is affinely equivalent to the normal fan of sections of a high dimensional positive orthant with well-chosen affine subspaces (see \cref{sec:typeCone}). We then observe that our algebraic result precisely states that all type cones of $\b{g}$-vector fans of cluster algebras are simplicial from which we derive all our geometric consequences (see \cref{sec:applications}).
\end{enumerate}

@@

\smallskip
\begin{enumerate}[$\quad\bullet$]
\item \textbf{Gentle associahedra} were constructed in~\cite{PaluPilaudPlamondon-nonkissing} as polytopal realizations of finite non-kissing complexes of gentle bound quivers.  These complexes encompass two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}. It was shown in~\cite{PaluPilaudPlamondon-nonkissing, BrustleDouvilleMousavandThomasYildirim} that the non-kissing complex of a gentle bound quiver provides a combinatorial model for the support $\tau$-tilting complex~\cite{AdachiIyamaReiten} of the associated gentle algebra. Even for finite non-kissing complexes, it turns out that the type cone of the non-kissing fan is not always simplicial (see \cref{exm:nonSimplicialTypeConeNKC}). We prove however that the type cone is always simplicial when the gentle bound quiver is brick (at least $2$ relations in any cycle) and $2$-acyclic (no oriented cycle of length~$2$). Moreover, we precisely describe the facet-defining inequalities of the type cone in terms of linear dependences of $\b{g}$-vectors involved in certain mesh relations. We thus automatically derive a construction similar to that of~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} describing all polytopal realizations of the $\b{g}$-vector fans of these brick $2$-acyclic bound quivers as sections of a positive orthant by well-chosen affine spaces (see \cref{subsec:typeConeCA}). Again, this result mainly relies on finding which relations minimally generate the relations between the $\b{g}$-vectors in the non-kissing complex. We present both a purely combinatorial proof (see \cref{subsec:typeConeCA}) and a purely algebraic proof for (non-necessarily gentle) brick algebras making use of extriangulated categories (see \cref{sec:extricats}).
Our algebraic proof is based on an analogue of a result of M. Auslander~\cite{Auslander1984} relating to minimal generators of Grothendieck groups.
Along the way, we need to generalise, for extriangulated categories, several results from cluster-tilting theory on indices~\cite{DehyKeller} and on abelian quotients~\cite{BuanMarshReiten, KellerReiten} that were known for triangulated categories.
We note however, that our assumptions are not quite the expected ones.
This is related to the fact that the Grothendieck groups of cluster categories are badly behaved (\eg the Grothendieck group of a cluster category of type~$A_2$ is trivial).
So as to overcome this difficulty, we replace the triangulated structure of cluster categories by some relative extriangulated structure, before considering Grothendieck groups.
This explains why we consider projective objects rather than cluster-tilting objects for extriangulated categories.

\medskip
\item \textbf{Graph associahedra} were defined by M.~Carr and S.~Devadoss~\cite{CarrDevadoss} in connection to C.~De Concini and C.~Procesi's wonderful arrangements~\cite{DeConciniProcesi}. As illustrated in~\cref{fig:specialGraphAssociahedra}, the graph associahedra of certain special families of graphs coincide with well-known families of polytopes: complete graph associahedra are permutahedra, path associahedra are classical associahedra, cycle associahedra are cyclohedra, and star associahedra are stellohedra. The graph associahedra were extended to the \defn{nestohedra}, which are simple polytopes realizing the nested complex of arbitrary building sets~\cite{Postnikov, FeichtnerSturmfels}. Graph associahedra and nestohedra have been geometrically realized in different ways: by successive truncations of faces of the standard simplex~\cite{CarrDevadoss}, as Minkowski sums of faces of the standard simplex~\cite{Postnikov, FeichtnerSturmfels}, or from their normal fans by exhibiting explicit inequality descriptions~\cite{Devadoss, Zelevinsky}. All these realizations have the same normal fan, called nested fan. We study the type cones of these nested fans (see \cref{subsec:typeConeGA}): we describe describe their facet-defining inequalities in terms of certain specific pairs of neighboring tubings and count them for the specific families of graph associahedra described earlier. For instance the type cone of the permutahedron coincides with the classical submodular functions on~$2^{[n]}$, described by~$2^{n-2} \binom{n}{2}$ inequalities. In fact, we observe that the type cone of a graphical nested fan is never simplicial except in the case of the classical associahedron (when the graph is the path). Our results describe nevertheless all polytopal realizations of the graphical nested fans.
\end{enumerate}

\smallskip
\enlargethispage{.5cm}
Further families of generalizations of the associahedron certainly deserve to be studied with our type cone approach.
We are investigating in particular brick polytopes~\cite{PilaudSantos-brickPolytope, PilaudStump-brickPolytope} and quotientopes~\cite{Reading-latticeCongruences, Reading-CambrianLattices, PilaudSantos-quotientopes}.
In fact, as already mentioned, it seems sometimes easier to find all polytopal realizations of a fan (by describing its type cone in terms of certain specific pairs of adjacent maximal cones) than to identify one specific explicit realization.
This is clearly the case when the type cone is simplicial as illustrated by the results of this paper: we naturally obtained all polytopal realizations of the $\b{g}$-vector fans of cluster algebras from cyclic seeds and of gentle algebras whose polytopality was only established very recently~\cite{HohlwegPilaudStella, PaluPilaudPlamondon-nonkissing}.
We believe that this gives reasonable hope that the polytopality of further fans could in the future be established using our type cone approach.
Tempting candidates are quotientopes for hyperplane arrangements beyond type~$A$, which are particularly interesting since the coarsenings of a fan essentially correspond to the faces of its type cone (see \cref{subsec:facesTypeCone}).

@@

\smallskip
\begin{enumerate}[$\quad\bullet$]
\item The facet-defining inequalities of the type cone of~$\Fan$ correspond to very specific pairs of adjacent maximal cones of~$\Fan$ whose corresponding linear dependences minimally generate all such dependences. While they correspond to mesh mutations for cluster algebras and brick $2$-acyclic gentle algebras, they are not clear in general (see for instance \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right)). It would be particularly interesting to fully understand these specific mutations for arbitrary ($\tau$-tilting finite) gentle algebras.

\smallskip
\item The rays of the type cone of~$\Fan$ correspond to specific polytopes which form a positive Minkowski basis of all realizations of~$\Fan$ (see \cref{subsec:MinkowskiSums}). In particular, when the type cone is simplicial, any polytopal realization of~$\Fan$ has a unique representation (up to translation) as a Minkowski sum of positive dilates of the polytopes corresponding to the rays of the type cone. For cluster algebras, it follows from~\cite[Sect.~6]{BazierMatteDouvilleMousavandThomasYildirim} that these polytopes are Newton polytopes of the $F$-polynomials. It would be interesting to obtain similar algebraic interpretations for the rays of the type cones of the non-kissing fans of gentle algebras.
\end{enumerate}
